---
title: "Plot DFE-alpha V. Trough Fitting scaled"
author: "Tom Booker"
date: "08/03/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
```

Start by reading in the libraries necessary for plotting the data and make my theme
```{r libraryPrep}
library(reshape2)
library(ggplot2)
library(wesanderson)
options(scipen=10000)
?wes_palette
pal <- wes_palette(n = 5, name = "Royal1", type = "continuous")
TommyTheme <-   
    theme_bw()+
    theme(
    axis.title.x = element_text(size=14,angle=0),
    axis.title.y = element_text(size=17,vjust=0.5),
    axis.text.x = element_text(size=12,angle=90),
    axis.text.y = element_text(size=12,angle=0),
    strip.text.y = element_text(size = 20, face = 'italic'),
    strip.text.x = element_text(size = 20, face = 'italic')
  )



```

Now i'm going to read in the data and prepare it for plotting 

```{r dataPrepBimodal}

rawBoots <- read.csv('analysis/BimodalSims.csv')
rawBoots$product1 <- rawBoots$NeSa1 * rawBoots$pa1
rawBoots$product2 <- rawBoots$NeSa2 * rawBoots$pa2
Boots<-melt(rawBoots, id = c('identifier'))

rawSims1 <- read.csv('analysis/BGS+SWEEPS/BimodalDFE.analysisScaled.txt')

Sims1<-melt(rawSims1, id = c('identifier','rep', 'AIC','Unnamed..0'))
Sims1$identifier <- 'Bimodal'

rawSims2 <- read.csv('analysis/BGS+SWEEPS/BimodalDFE_div10.analysisScaled.txt')
Sims2<-melt(rawSims1, id = c('identifier','rep', 'AIC','Unnamed..0'))
Sims2$identifier <- 'Bimodal_div10'

rawSims3 <- read.csv('analysis/BGS+SWEEPS/BimodalDFE_div100.analysisScaled.txt')
Sims3<-melt(rawSims1, id = c('identifier','rep', 'AIC', 'Unnamed..0'))
Sims3$identifier <- 'Bimodal_div100'

Sims <- rbind(Sims1,Sims2,Sims3)

bimLabs <- c("NeSa1","NeSa2","pa1","pa2","product1","product2")

Sims$variable <- factor(Sims$variable, levels = bimLabs,
                 labels = bimLabs)
Boots$variable <- factor(Boots$variable, levels = bimLabs,
                 labels = bimLabs)
Sims$source <- 'Trough-Fitting'

selRaw <- read.csv('dfe-alpha/Bimodal_selectedSites.csv')
sel<-melt(selRaw,c("Es","L","N1","N2","N3","Nw","f0", "f2n","identifier", "b",  "rep", "sa.0.","pa.0.","sa.1.","pa.1.","t2","t3"))
sel$source <- 'DFE-alpha'

sel$ID<-paste(sel$identifier)
Sims$ID<-paste(Sims$identifier)

nSims <- subset(Sims, select=c('variable', 'value', 'ID', 'source'))
nsubset<- subset(sel, select=c('variable', 'value', 'ID', 'source'))
new<- rbind(nSims,nsubset)

vnames <-list(
  'NeSa1' = expression(gamma[a(1)]),
  'NeSa2' = expression(gamma[a(2)]),
  'pa1' = expression(p[a(1)]),
  'pa2' = expression(p[a(2)]),
  'product1' = expression(gamma*p[a(1)]),
  'product2' = expression(gamma*p[a(2)]),
  'DFE-alpha' = 'DFE-alpha',
  'Trough-Fitting' = 'Trough-Fitting')


vlabeller <- function(variable,value){
  return(vnames[value])
}

```

Let's get this show on the road and plot 

```{r fig.width=10, fig.height=8,echo=FALSE}

ggplot(data = new, aes( x = ID, y =  log10(value), col = source))+
  geom_violin( size = 0.8)+
  geom_point(data= Boots, aes( x = identifier, y = log10(1), col = 'True\nValue'), shape = '_', size = 15)+
  facet_grid( source ~ variable, scales = 'free', labeller = vlabeller)+
 #  stat_summary(fun.y = median, fun.ymin = min, fun.ymax = max, colour = pal[3])+
  scale_y_log10(expression(log[10] * '(est/sim)'))+
  scale_x_discrete('')+
  scale_color_manual('',values = pal)+
  ggtitle('Bimodal DFE')+
  TommyTheme

```

```{r dataPrepFixed,echo=FALSE}


rawBoots <- read.csv('~/PhD/Coding/Estimate_selection_from_troughs/simulations/analysis/fixedClassSims.csv')
rawBoots$product <- rawBoots$NeSa * rawBoots$pa
Boots<-melt(rawBoots, id = c('identifier'))

rawSims1 <- read.csv('~/PhD/Coding/Estimate_selection_from_troughs/simulations/analysis/BGS+SWEEPS/Nes10_dDFE.Exponential_div10.analysisScaled.txt')
rawSims1$product <- rawSims1$NeSa * rawSims1$pa
Sims1<-melt(rawSims1, id = c('identifier','X','rep', 'AIC'))
Sims1$identifier <- 'Nes10 - div10'

rawSims2 <- read.csv('~/PhD/Coding/Estimate_selection_from_troughs/simulations/analysis/BGS+SWEEPS/Nes10_dDFE.Exponential.analysisScaled.txt')
rawSims2$product <- rawSims2$NeSa * rawSims2$pa
Sims2<-melt(rawSims2, id = c('identifier','X','rep', 'AIC'))
Sims2$identifier <- 'Nes10'

rawSims3 <- read.csv('~/PhD/Coding/Estimate_selection_from_troughs/simulations/analysis/BGS+SWEEPS/Nes200_dDFE.Exponential_div10.analysisScaled.txt')
rawSims3$product <- rawSims3$NeSa * rawSims3$pa
Sims3<-melt(rawSims3, id = c('identifier','X','rep', 'AIC'))
Sims3$identifier <- 'Nes200 - div10'

rawSims4 <- read.csv('~/PhD/Coding/Estimate_selection_from_troughs/simulations/analysis/BGS+SWEEPS/Nes200_dDFE.Exponential.analysisScaled.txt')
rawSims4$product <- rawSims4$NeSa * rawSims4$pa
Sims4<-melt(rawSims4, id = c('identifier','X','rep', 'AIC'))
Sims4$identifier <- 'Nes200'

Sims <- rbind(Sims1,Sims2,Sims3,Sims4)
str(Sims)
bimLabs <- c("NeSa","pa","product")

Sims$variable <- factor(Sims$variable, levels = bimLabs,
                 labels = bimLabs)
Boots$variable <- factor(Boots$variable, levels = bimLabs,
                 labels = bimLabs)
Sims$source <- 'Trough-Fitting'

selRaw <- read.csv('dfe-alpha/Nes_selectedSites.csv')

sel<-melt(selRaw,c("Es","L","N1","N2","N3","Nw","f0", "f2n","identifier", "b",  "rep", "sa.0.","pa.0.","t2","t3"))
sel$source <- 'DFE-alpha'

sel$ID<-paste(sel$identifier)
Sims$ID<-paste(Sims$identifier)

nSims <- subset(Sims, select=c('variable', 'value', 'ID', 'source'))
nsubset<- subset(sel, select=c('variable', 'value', 'ID', 'source'))
new<- rbind(nSims,nsubset)

vnames <-list(
  'NeSa' = expression(gamma[a]),
  'pa' = expression(p[a]),
  'product' = expression(gamma*p[a]),
  'DFE-alpha' = 'DFE-alpha',
  'Trough-Fitting' = 'Trough-Fitting')


vlabeller <- function(variable,value){
  return(vnames[value])
}

```

```{r fig.width=7, fig.height=10,echo=FALSE}
new$value <- round(new$value*1e8)/1e8

ggplot(data = new, aes( x = ID, y =  value, col = source))+
  geom_violin(size = 0.8)+
  geom_point(data= Boots, aes( x = identifier, y = value, col = 'True\nValue'), shape = '_', size = 15)+
  facet_grid(variable~source , scales = 'free',  labeller = vlabeller)+
#   stat_summary(fun.y = median, fun.ymin = min, fun.ymax = max, colour = pal[3])+
  scale_y_log10('')+
  scale_x_discrete('')+
  scale_color_manual('',values = pal)+
  ggtitle('Fixed-Class DFE')+
  TommyTheme


```

Now let's plot the results from the demographic comparison

I'll plot likelihood differences, so keep in mind that between the 2- and 3-epoch models there is a difference of 2 parameters. This means that the threshold for statisitcal significance is a value of 2 * likelihood difference is 5.99

```{r plotDemographic}

demo <- read.csv('dfe-alpha/DemographicAnalysis.csv')
demo$ratio3 <- demo$N3/demo$N1
demo$ratio2 <- demo$N2/demo$N1
demo$ratio1 <- demo$N1/demo$N1

vars <- c("L","N1","N2","N3","Nw","dL", "epochs", "f0", "f2n", "t2", "t3", "model") 
#vars <- c("L","N1","N2","N3","Nw", "epochs", "f0", "f2n", "t2", "t3", "model") 
newDemo <- melt(demo, id = vars)
#newDemo <- demo #melt(demo, id = vars)
newDemo$Epochs <- as.factor(newDemo$epochs)
library(ggplot2)


ggplot(data = newDemo, aes(x = model, y = 2*dL, col = Epochs ))+
  geom_point(size = 2)+
  scale_color_manual('# Epochs',values = pal)+
  geom_hline(yintercept=5.99, alpha = 0.5, lty = 2)+
  scale_y_log10(expression('2'*Delta * 'lnL'))+
  scale_x_discrete('')+
  TommyTheme+
  coord_flip()

```

# Now plot polyDFE stuff

```{r polyDFE plotting}
rm(list=ls())

pal <- wes_palette(n = 5, name = "Royal1", type = "continuous")
TommyTheme <-   
    theme_bw()+
    theme(
    axis.title.x = element_text(size=14,angle=0),
    axis.title.y = element_text(size=17,vjust=0.5),
    axis.text.x = element_text(size=12,angle=90),
    axis.text.y = element_text(size=12,angle=0),
    strip.text.y = element_text(size = 20, face = 'italic'),
    strip.text.x = element_text(size = 20, face = 'italic')
  )


polyDFEraw = read.csv('run_polyDFE/ExponentialPolyDFE.csv')
polyDFE <- melt(polyDFEraw, id = c('model', 'number', 'b','S_d'))
polyDFE$identifier <- polyDFE$model

polyDFE$source <- 'polyDFE'

Trough1raw<- read.csv('analysis/BGS+SWEEPS/Exp.Nes100_dDFE.Exponential.analysisScaled.txt')
Trough1raw$product<-Trough1raw$NeSa*Trough1raw$pa
Trough1<-melt(Trough1raw, id = c('AIC','identifier','rep','X'))
Trough1$identifier<- 'Exp100'
Trough1$source <- 'Trough-Fitting'

Trough2raw<- read.csv('analysis/BGS+SWEEPS/Exp.Nes100_dDFE.Exponential_div10.analysisScaled.txt')
Trough2raw$product<-Trough2raw$NeSa*Trough2raw$pa
Trough2<-melt(Trough2raw, id = c('AIC','identifier','rep','X'))
Trough2$identifier<- 'Exp100 - div10'
Trough2$source <- 'Trough-Fitting'

Trough3raw<- read.csv('analysis/BGS+SWEEPS/Exp.Nes10_dDFE.Exponential.analysisScaled.txt')
Trough3raw$product<-Trough3raw$NeSa*Trough3raw$pa
Trough3<-melt(Trough3raw, id = c('AIC','identifier','rep','X'))
Trough3$identifier<- 'Exp10'
Trough3$source <- 'Trough-Fitting'

Trough4raw<- read.csv('analysis/BGS+SWEEPS/Exp.Nes10_dDFE.Exponential_div10.analysisScaled.txt')
Trough4raw$product<-Trough4raw$NeSa*Trough4raw$pa
Trough4<-melt(Trough4raw, id = c('AIC','identifier','rep','X'))
Trough4$identifier<- 'Exp10 - div10'
Trough4$source <- 'Trough-Fitting'

Troughs <- rbind(Trough1, Trough2, Trough3, Trough4)

rawExp <- read.csv('~/PhD/Coding/Estimate_selection_from_troughs/simulations/analysis/expSims.csv')
rawExp$product = rawExp$NeSa * rawExp$pa
Exp <- melt(rawExp, id = 'identifier')

vnames <-list(
  'NeSa' = expression(gamma[a]),
  'pa' = expression(p[a]),
  'product' = expression(gamma*p[a]),
  'polyDFE' = 'polyDFE',
  'Trough-Fitting' = 'Trough-Fitting')


vlabeller <- function(variable,value){
  return(vnames[value])
}
```

```{r fig.width=16, fig.height=20,echo=FALSE}
Troughs$value <- round(Troughs$value*1e8)/1e8
polyDFE$value <- round(polyDFE$value*1e8)/1e8

# ggplot(data = polyDFE , aes (x = identifier, y = value, col = source))+
#   geom_boxplot(fill= source)+
#   geom_boxplot(data = Troughs, aes( x = identifier, y = value, col = source))+
#   geom_point(data= Exp, aes( x = identifier, y = value, col = 'True\nValue'), shape = '_', size = 15)+
#   facet_grid(variable~source, scales = 'free', labeller = vlabeller)+
#   scale_y_log10('')+
#   scale_x_discrete('')+
#   scale_color_manual('',values = pal)+
#   ggtitle('Exponential DFE')+
#   TommyTheme
```
